---
title: "BulkSignalR : </br> Inference of ligand-receptor interactions 
from bulk data or spatial transcriptomics"
author:
  - name: Jean-Philippe Villemin
    affiliation:
    - Institut de Recherche en Cancérologie de Montpellier,
     Inserm, Montpellier, France 
    email: jean-philippe.villemin@inserm.fr
  - name: Jacques Colinge
    affiliation:
    - Institut de Recherche en Cancérologie de Montpellier,
     Inserm, Montpellier, France 
    email: jacques.colinge@inserm.fr
date: "`r format(Sys.Date(), '%m/%d/%Y')`"
output: 
  rmarkdown::html_vignette:
      self_contained: true
      toc: true
      toc_depth: 4
      highlight: pygments
      fig_height: 3
      fig_width: 3
      fig_caption: no
      code_folding: show
package: BulkSignalR
vignette: >
  %\VignetteIndexEntry{BulkSignalR-Configure}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::knit_hooks$set(optipng = knitr::hook_optipng)
options(rmarkdown.html_vignette.check_title = FALSE)
```
```{r load-libs, message = FALSE,  warning = FALSE, results = FALSE}
library(BulkSignalR)
```

## Configure local cache and hidden environment variables

`BulkSignalR` donwload resource files just once after the first 
installation.  

Several data versions can be access remotely from :
[here](https://partage-dev.montp.inserm.fr:9192/CBSB/SignalR/resources/)
These datasets can be used to reset the sources locally.  

A mecanism handled by `BioCFileCache` package informs the user 
if the local files are up to date. 
Several functions as `cacheVersion` and `cacheInfo` give
informations about the content of the local cache and its synchronization 
state  with its remote source.  

Cache directory can be cleaned by `cacheClear` function and and forced to be 
created again using `createResources(onRequest=TRUE)`. Otherwise it will be
automatically recreated when the package is next loaded.   

The knowledge database (pathways - GO-BP / Reactome, Ligand &
recepors - LRdb, and gene Network are handled inside a hidden environment 
variable  called `.SignalR`)

The sources can be rewritten using `resetPathways`, `resetLRdb` 
and `resetNetwork`.  

```{r cash,eval=True}

# You can see hidden environment variable list as follows.
ls("BulkSignalR:::.SignalR")

# Setup Pathways for reactome (can be done for GO-BP also)

subset <- c("REACTOME_BASIGIN_INTERACTIONS",
"REACTOME_SYNDECAN_INTERACTIONS",
"REACTOME_ECM_PROTEOGLYCANS",
"REACTOME_CELL_JUNCTION_ORGANIZATION")

reactSubset <- BulkSignalR:::.SignalR$BulkSignalR_Reactome[
BulkSignalR:::.SignalR$BulkSignalR_Reactome$`Reactome name` %in% subset,]

resetPathways(dataframe = reactSubset,
resourceName = "Reactome")

cacheInfo()
cacheVersion()

# Empty local cache
cacheClear()

cacheInfo()
cacheVersion()

# Ask for download
createResources(onRequest=TRUE)

cacheInfo()

dim(BulkSignalR:::.SignalR$BulkSignalR_LRdb)

# Set up LRdb
df <- data.frame(
  ligand    = c("A2M", "AANAT", "AANAT", "ACE", "ACE"),
  receptor  = c("LRP1", "MTNR1A", "MTNR1B", "AGTR2", "BDKRB2")
)
resetLRdb(df,switch=TRUE)

dim(.SignalR$BulkSignalR_LRdb)

# Set up Network

dim(.SignalR$BulkSignalR_Network)

df <- data.frame(
  a.gn   = c("A2M", "AANAT", "AANAT", "ACE", "ACE"),
  type  = c("regulates-transcription-of",
   "regulates-transcription-of",
   "regulates-transcription-of", 
   "regulates-transcription-of", 
   "regulates-transcription-of"),
  b.gn  = c("LRP1", "MTNR1A", "MTNR1B", "AGTR2", "BDKRB2")
)

resetNetwork(network)
dim(.SignalR$BulkSignalR_Network)


```  

\
    
Thank you for reading this guide and for using `BulkSignalR`.  

\

## Session Information

```{r session-info}
sessionInfo()
```
